Comprehensive optical and data management infrastructure for high-throughput light-sheet microscopy of whole mouse brains

### 2015-03-27 Neurophotonics/Stuff/manuscript1.1_Caro.tex
commit before revision process

\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{PanelSampel.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:Panel0} (A) Schematic of light sheet microscopy. Excitation (blue) and fluorescence detection (green) occur on independent, perpendicular axes. (B) Mounting of a clarified, fluorescently labelled brain. The brain is glued onto a coverslip and inserted into an adapter that slides into a Teflon cylinder.} 
   \end{figure}

@@

To acquire whole brain data sets, we fix a clarified and fluorescently-labelled mouse brain with super glue to a coverslip (Figure\ref{fig:Panel0},B). The brain is oriented along its axial orientation with the olfactory bulbs at the top and the cerebellum at the bottom of the coverslip. The coverslip is slid into a bottom adaptor and tightened with a plastic-capped grub screw. The bottom adaptor is inserted into a Teflon cylinder with the coverslip being positioned on the far side of the detection objective. Three different slits in the adapter correspond to varying distances to the detection objective and give variability in sample thickness for example to allow also for the mounting of rat brain hemispheres.

@@

The scan mirror surface is re-imaged with a telescope (f50, f100) onto the back aperture of a long working distance, low magnification objective (Nikon, 10x 0.3NA WD 17.5mm). The two excitation objectives are designed for air immersion but are immersed into the clearing solution within the sample chamber. A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the front lens elements from the organic solvent. The light sheet is generated digitally\cite{Keller2008a,Keller2008b} by scanning the excitation beam across the focal plane of the detection objective. %This generates perfectly incoherent illumination resulting in fewer artefacts.%cite{StelzerNatMeth2014}.

\subsection{Detection}
		%objective, camera, rolling shutter. Use references\cite{Silvestri2012} to old SPIM.
		%exposure time of single line affects how many are exposed at same time, confocality by synchronisation- not exactly

@@

In it's simplest form, the fluorescence detection unit of a light sheet microscope is a conventional wide-field microscope: an objective lens, a fluorescent filter and a tube lens for an image on a wide-field detector. Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions. The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP). To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging. A tube lens of 200mm creates the primary image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a chip of over 4 megapixels. In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other. In the rolling shutter data acquisition mode only a subset of adjacent horizontal pixel lines is simultaneously exposed and this active detection region is moved across the image sensor. With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($9.7\micro s$, see Table\ref{tab:resolution}) the entire frame of 2048 horizontal lines is activated within 19.86ms. Setting the line exposure time to 3ms results in approx. 300 lines being simultaneously exposed. This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of $80\micro m$ in the sample space. With those values the camera acquires images at a frame rate of 44Hz.

@@

\begin{landscape}
\begin{table}[t!]
	\centering
		\caption[Resolution]{Imaging properties and derived quantities. The thickness of the light sheet is approximately of the same size as the depth of field of the high NA detection lens.\label{tab:resolution}}
		\begin{tabular}{lrlrl}
		\multicolumn{5}{l}{Detection}\\\hline\hline
		wavelength																	&	$\lambda$				&																																					& 0.5			& $\mu m$	\\
		refractive index														&	n								&																																					& 1.45		& 				\\
		numerical aperture 													&	$\text{NA}_d$		&																																					& 1				& 				\\
		angular aperture 														& $\alpha$				&	$=sin^{-1}(\nicefrac{\text{NA}_d}{n})$																	& 43.6		& $deg$		\\
		magnification 															& M								&																																					& 25			&					\\
		tube lens 																	& $f_{\text{TL}}$	&																																					& 180			&	$mm$		\\
		effective focal length objective						& EFL							& $=\nicefrac{f_{\text{TL}}}{M}$																					& 7.2			& $mm$		\\
		diameter back focal plane										& BFP							& $= 2\text{EFL}\text{NA}_d$																							& 14.4		& $mm$		\\
		field number																& FN							&																																					& 18			& $mm$		\\
		field size in specimen											& S								& $=\nicefrac{\text{FN}}{M}$																							& 0.72		& $mm$		\\
		depth of field															& $\Delta$				& $=\nicefrac{\lambda*n}{(\text{NA}_d)^2}+ \nicefrac{n*e}{M \text{NA}_d}$	& 1.10 		& $\mu m$	\\ 
		Airy radius lat.														& $r_A$						& $=\nicefrac{0.61 \lambda}{\text{NA}_d}$																	& 0.31		& $\mu m$	\\\\
		\multicolumn{5}{l}{Excitation}\\\hline\hline
		numerical aperture 													&	$\text{NA}_e$		&																																					& 0.3			& 				\\
		magnification,	nominal											& m								&																																					& 10			&					\\
		tube lens 																	& $f_{\text{tl}}$	&																																					& 100			&	$mm$		\\
		effective focal length, objective						& efl							& $=\nicefrac{f_{\text{tl}}}{m}$																					& 20			& $mm$		\\
		magnification, effective										& $m_e$						&	$=\nicefrac{f_{\text{tl}}}{\text{efl}}$																	& 5				&					\\
		refractive index														&	$\eta$					&																																					& 1				& 				\\
		beam radius																	& $\omega$				&																																					& 4.5			& $mm$		\\
		%Airy radius lat.														& $r_a$						& $=\nicefrac{0.61 \lambda}{\text{NA}_e}$																	& 1.02		& $\mu m$	\\
		min light sheet waist												& $\omega_0$			& $=\nicefrac{\lambda \text{efl}}{\pi \omega}$														& 1.41		& $\mu m$	\\
		confocal parameter													& b								& $=\nicefrac{2 \pi \omega_0^2}{\lambda}$																	& 25.15		& $\mu m$	\\\\
		\multicolumn{5}{l}{Camera}\\\hline\hline
		cell size																		& e								&																																					& 6.5			&	$\mu m$	\\
		effective area 															& $r^2$						&																																					& $13.3^2$	&	$\text{mm}^2$	\\
		line read out time													& t								&																																					& 9.7			&	$\mu s$	\\
		line exposure time													& l								&																																					& 3				&	ms			\\
		slit width, camera space										& $d_c$						& $=\nicefrac{l}{t} $																											& 2				&	mm	\\
		slit width, sample space										& $d_s$						&	$=\nicefrac{d_c}{M}$																										& 80			&	$\mu m$	\\
		frame rate																	& $\nu$						&	$=\nicefrac{1}{2048 t + l}$																							& 43.6		& Hz\\
		\end{tabular}
\end{table}
\end{landscape}

>>>>

\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{PanelSampel.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:Panel0} (A) Schematic of light sheet microscopy. The sample is illuminated with a planar light sheet (blue) perpendicular to fluorescence detection (green). (B) Mounting of a clarified, fluorescently labelled brain. The brain is glued onto a coverslip and inserted into an adapter that slides into a Teflon cylinder.} 
   \end{figure}

@@

For the acquisition of whole brain data sets, we fix a clarified and fluorescently-labelled mouse brain with super glue to a coverslip (Figure\ref{fig:Panel0},B). The brain is oriented along its axial orientation with the olfactory bulbs at the top and the cerebellum at the bottom of the coverslip. The coverslip is slid into a bottom adaptor and tightened with a plastic-capped grub screw. The bottom adaptor is inserted into a Teflon cylinder with the coverslip being positioned on the far side of the detection objective. Three different slits in the adapter correspond to varying distances to the detection objective and give variability in sample thickness for example to allow also for the mounting of rat brain hemispheres.

@@

The scan mirror surface is re-imaged with a telescope (f50, f100) onto the back aperture of a long working distance, low magnification objective (Nikon, 10x 0.3NA WD 17.5mm). The two excitation objectives are designed for air immersion but are immersed into the clearing solution within the sample chamber. A coverslip glued to the front housing edge serves the dual purpose of maintaining the first diffractive surface between the front optical element and the air and to protect the front lens elements from the organic solvent. The light sheet is generated digitally\cite{Keller2008a,Keller2008b} by scanning the excitation beam across the focal plane of the detection objective. This generates incoherent illumination resulting in fewer artefacts.%cite{StelzerNatMeth2014}.
Additionally each line is specimen is illuminated with the same intensity creating a homogeneous light sheet which is particularly advantageous for the quantitative investigation of large samples in their entirety.

\subsection{Detection unit}
		%objective, camera, rolling shutter. Use references\cite{Silvestri2012} to old SPIM.
		%exposure time of single line affects how many are exposed at same time, confocality by synchronisation- not exactly

@@

In it's simplest form, the fluorescence detection unit of a light sheet microscope is a conventional wide-field microscope: an objective lens, a fluorescent filter and a tube lens for an image on a wide-field detector. Fluorescence is collected with an objective that is specifically designed for immersion in clearing solutions. The objective is equipped with a correction collar allowing for immersion in media with refractive indices ranging from 1.41 to 1.52 (Olympus, XLSLPLN25XGMP). To image the whole volume of interest the objective has a relatively low magnification of 25x and a large working distance of 8mm yet a high numerical aperture (1.0NA) affords high resolution imaging. A tube lens of 200mm creates the primary image on a sCMOS camera (Orca Flash4.0, Hamamatsu) with a chip of over 4 megapixels. In contrast to CCD sensors each pixel of a sCMOS camera sensor has a separate photodetector and amplification unit which means that sCMOS pixels can be read out independently from each other. The cell size of the OrcaFlash is $p^2= 6.5\micro m$ x $6.5\micro m$ over an active area of 13.3mm. With a 200mm tube lens the field of view in the sample is $480\micro m$.

In the rolling shutter data acquisition mode only a subset of adjacent horizontal pixel lines is simultaneously exposed and this active detection region is moved across the image sensor. With the delay between the exposure of two adjacent lines set to the minimum time required to read out a single line ($t=9.7\micro s$, see Table\ref{tab:resolution}) the entire frame of 2048 horizontal lines is activated within 19.86ms. Setting the line exposure time to $l=3ms$ results in approx. $k=\nicefrac{l}{t}\approx300$  lines being simultaneously exposed at any time. This detection area is swept from the top to the bottom of the chip and acts like a moving, virtual confocal slit corresponding to a width of $d_s=\nicefrac{k p}{M_{\text{eff}}}= 0.72m$ in the sample space. With the given values of line exposure and line read out time, the camera acquires images at a frame rate of $\nu = \nicefrac{1}{(2048t+l)} \approx 44Hz$.

@@

\begin{landscape}
\begin{table}[t!]
	\centering
		\caption[Resolution]{Imaging properties and derived quantities. The thickness of the light sheet is approximately of the same size as the depth of field of the high NA detection lens.\label{tab:resolution}}
		\begin{tabular}{lrlrl}
		\multicolumn{5}{l}{Detection}\\\hline\hline  
		wavelength																	&	$\lambda$				&																																					& 0.5			& $\mu m$	\\
		refractive index														&	n								&																																					& 1.45		& 				\\
		numerical aperture 													&	$\text{NA}_d$		&																																					& 1				& 				\\
		%angular aperture 													& $\alpha$				&	$=sin^{-1}(\nicefrac{\text{NA}_d}{n})$																	& 43.6		& $deg$		\\
		magnification 															& $M_{\text{eff}}$&	$= \nicefrac{f_{\text{TL}}}{\text{EFL}}$																& 27.8		&					\\
		tube lens 																	& $f_{\text{TL}}$	&																																					& 200			&	$mm$		\\
		effective focal length objective						& EFL							& $=\nicefrac{f_{\text{TL}}}{M}$																					& 7.2			& $mm$		\\
		diameter back focal plane										& BFP							& $= 2\cdot \text{EFL} \cdot \text{NA}_d$																	& 14.4		& $mm$		\\
		field number																& FN							&																																					& 18			& $mm$		\\
		field size in specimen											& S								& $=\nicefrac{\text{FN}}{M}$																							& 0.65		& $mm$		\\
		depth of field															& $\Delta$				& $=\nicefrac{\lambda \cdot n}{(\text{NA}_d)^2}+ \nicefrac{n \cdot e}{M \cdot \text{NA}_d}$	& 1.06 		& $\mu m$	\\ 
		Airy radius lat.														& $r_A$						& $=\nicefrac{0.61 \lambda}{\text{NA}_d}$																	& 0.31		& $\mu m$	\\\\
		\multicolumn{5}{l}{Excitation}\\\hline\hline
		numerical aperture 													&	$\text{NA}_e$		&																																					& 0.3			& 				\\
		magnification,	nominal											& m								&																																					& 10			&					\\
		tube lens 																	& $f_{\text{tl}}$	&																																					& 100			&	$mm$		\\
		effective focal length, objective						& efl							& $=\nicefrac{f_{\text{tl}}}{m}$																					& 20			& $mm$		\\
		magnification, effective										& $m_e$						&	$=\nicefrac{f_{\text{tl}}}{\text{efl}}$																	& 5				&					\\
		refractive index														&	$\eta$					&																																					& 1				& 				\\
		beam radius																	& $\omega$				&																																					& 4.5			& $mm$		\\
		%Airy radius lat.														& $r_a$						& $=\nicefrac{0.61 \lambda}{\text{NA}_e}$																	& 1.02		& $\mu m$	\\
		min light sheet waist												& $\omega_0$			& $=\nicefrac{\lambda \text{efl}}{\pi \omega}$														& 1.41		& $\mu m$	\\
		confocal parameter													& b								& $=\nicefrac{2 \pi \omega_0^2}{\lambda}$																	& 25.15		& $\mu m$	\\\\
		\multicolumn{5}{l}{Camera}\\\hline\hline
		cell size																		& e								&																																					& 6.5			&	$\mu m$	\\
		effective area 															& $r^2$						&																																					& $13.3^2$	&	$\text{mm}^2$	\\
		line read out time													& t								&																																					& 9.7			&	$\mu s$	\\
		line exposure time													& l								&																																					& 3				&	ms			\\
		slit width, camera space										& $d_c$						& $=\nicefrac{l \cdot e}{t} $																							& 2				&	mm	\\
		slit width, sample space										& $d_s$						&	$=\nicefrac{d_c}{M}$																										& 0.72		&	mm	\\
		frame rate																	& $\nu$						&	$=\nicefrac{1}{(2048 \cdot t + l})$																			& 43.6		& Hz\\
		\end{tabular}
\end{table}
\end{landscape}

### 2015-03-27 Neurophotonics/Stuff/manuscript_snellendo_merged.tex
commit before revision process

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{abstract}
The comprehensive mapping and quantification of neuronal projections in the central nervous system requires high-throughput imaging of large volumes with microscopic resolution. We have developed a confocal light-sheet microscope that has been optimised for the 3D imaging of structurally intact clarified whole-mount mouse brains. Here we describe the optical and electro-mechanical arrangement of the microscope and give details on the organisation of the microscope management software. The software orchestrates all components of the microscope, coordinates critical timing and synchronisation and has been written in a versatile and modular structure using the LabVIEW language.  It can easily be adapted and integrated to other microscope systems and has been made freely available to the light-sheet community. The tremendous amount of data routinely generated by light-sheet microscopy further requires novel strategies for data handling and storage. To complete the full imaging pipeline of our high- throughput microscope we further elaborate on big data management from the data streaming of raw images up to stitching and visualisation of 3D data sets. The meso-scale neuroanatomy imaged at micron-scale resolution in those datasets allows characterization and quantification of neuronal projections in unsectioned mouse brains. 
\end{abstract}

@@

The highly ambitious project of mapping and understanding each and every neuronal projection in the whole brain has been moved to feasible reality by the recent advent of light-sheet fluorescent microscopy (LSFM)\cite{Huisken2004,Dodt2007,Keller2012}. With this technique 3D data sets can be acquired with a resolution that is high enough to identify neurons and their dendritic, axonal features in time scales which are no longer the bottle neck of high-throughput acquisition. In LSFM, the sample is illuminated with a thin sheet of light confined into the focal plane of the detection objective, which collects the fluorescence emission along an axis perpendicular to the illumination plane\cite{Huisken2009}. This technique drastically reduces the imaging acquisition time by recording millions of pixels in parallel due to its wide-field detection and affords intrinsic optical sectioning due to the light-sheet illumination. Consequently fluorophores outside the light-sheet are neither bleached nor contribute blurring out-of-focus noise. Together these attributes cause a high spatio-temporal resolution and an excellent signal to noise ratio in LSFM.

@@

Here we will present a state-of-the-art light-sheet microscope, as it is implemented in our lab, that is especially well suited to acquire 3D data sets of large clarified and structurally intact mouse brains. The LSFM features double-sided illumination with a digitally scanned light-sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$) immersed and freely movable samples. After briefly introducing the optical setup we explain how to prepare and mount the samples for stable, 3D imaging for several days. In addition, a full description of the control hardware and software is presented. The microscope software coordinates every microscope component and ensures critical timing and synchronisation between those components. %The software code has been implemented using a versatile and modular scheme in the LabVIEW language and has been made freely available to the light-sheet community. 
We further give a systematic and robust approach to handle, store and analyse light-sheet microscopy data of several terabytes. To conclude the comprehensive and high-throughput imaging pipeline we furthermore elaborate on stitching and visualisation of large 3D data sets. The imaging capabilities of our light-sheet microscope are exemplified with tomographies of whole transgenic mouse brains.

@@

Light sheet microscopy has already been a game changer for large-scale, high-throughput imaging by yielding data with a high spatio-temporal scale. This measurement technique will continue to have a high impact in the field of whole brain imaging due to its ability to record millions of images over the course of days or even weeks. Here we have presented a complete and detailed framework for whole mouse brain imaging. Starting with a full description of our double-sided light sheet microscope and its constituent components we further gave details of the custom-written control software which coordinates the microscope's reliably synchronised operation. The data produced in our experiments easily amounts several TB per data set and needs to be compressed, stored, transferred, retrieved andF processed necessitating the concurrent development of novel computational interface and analysis methods. Here we have presented a comprehensive, robust and fully automated pipeline of data management starting from the streaming of raw images up to the stitching of 3D data sets.

@@

Additionally another problem inherent to light sheet microscopy degrades image quality: due to the uncoupled nature of excitation and detection in LSFM, the aberrations encountered in each arm are independent too and this can lead to a walk-off between the light-sheet and the detection FOV when large samples are imaged at depths. Adaptive optics\cite{Booth2007} provides a means to compensate for these aberrations and has recently been applied to improve LSFM\cite{Jorand2012,Wang2014}. The prospect of high quality images is especially essential for high through-put imaging methods like light-sheet microscopy and whole brain 3D reconstruction because the size of data sets are so large they warrant fully automated post processing for example for automated cell counting and identification\cite{Frasconi2014}. The effect of optical aberrations can severely obscure features even above the resolution limit and therefore hinder automated segmentation of the data. We have mounted the camera on a separate breadboard which leaves us with a lot of free, infinity-corrected space in the detection path. The implementation of adaptive optics technology into the fluorescence emission path of our LSFM in order to demonstrate real-time aberration corrected images for whole brain reconstructions will be considered in the future.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\begin{abstract}
The comprehensive mapping and quantification of neuronal projections in the central nervous system requires high-throughput imaging of large volumes with microscopic resolution. We have developed a confocal light-sheet microscope that has been optimised for the 3D imaging of structurally intact clarified whole-mount mouse brains. Here we describe the optical and electro-mechanical arrangement of the microscope and give details on the organisation of the microscope management software. The software orchestrates all components of the microscope, coordinates critical timing and synchronisation and has been written in a versatile and modular structure using the LabVIEW language.  It can easily be adapted and integrated to other microscope systems and has been made freely available to the light-sheet community. The tremendous amount of data routinely generated by light-sheet microscopy further requires novel strategies for data handling and storage. To complete the full imaging pipeline of our high- throughput microscope we further elaborate on big data management from the data streaming of raw images up to stitching of 3D data sets. The meso-scale neuroanatomy imaged at micron-scale resolution in those datasets allows characterization and quantification of neuronal projections in unsectioned mouse brains. 
\end{abstract}

@@

The highly ambitious project of mapping and understanding each and every neuronal projection in the whole brain has been moved to feasible reality by the recent advent of light-sheet fluorescent microscopy (LSFM)\cite{Huisken2004,Dodt2007,Keller2012}. With this technique 3D data sets can be acquired with a resolution that is high enough to identify neurons and their dendritic and axonal features in time scales which are no longer the bottle neck of high-throughput acquisition. In LSFM, the sample is illuminated with a thin sheet of light confined into the focal plane of the detection objective, which collects the fluorescence emission along an axis perpendicular to the illumination plane\cite{Huisken2009}. This technique drastically reduces the imaging acquisition time by recording millions of pixels in parallel due to its wide-field detection and affords intrinsic optical sectioning due to the light-sheet illumination. Consequently fluorophores outside the light-sheet are neither bleached nor contribute blurring out-of-focus noise. Together these attributes cause a high spatio-temporal resolution and an excellent signal to noise ratio in LSFM.

@@

Here we will present a state-of-the-art light-sheet microscope, as it is implemented in our lab, that is especially well suited to acquire 3D data sets of large clarified and structurally intact mouse brains. The LSFM features double-sided illumination with a digitally scanned light-sheet and a sample chamber which has been specifically designed for the the imaging of large ($> 1cm^3$) immersed and freely movable samples. After briefly introducing the optical setup we explain how to prepare and mount the samples for stable, 3D imaging for several days. In addition, a full description of the control hardware and software is presented. The microscope software coordinates every microscope component and ensures critical timing and synchronisation between those components. %The software code has been implemented using a versatile and modular scheme in the LabVIEW language and has been made freely available to the light-sheet community. 
We further give a systematic and robust approach to handle and store light-sheet microscopy data of several terabytes. To conclude the comprehensive and high-throughput imaging pipeline we furthermore elaborate on stitching of large 3D data sets. The imaging capabilities of our light-sheet microscope are exemplified with tomographies of whole transgenic mouse brains.

@@

Light-sheet microscopy has already been a game changer for large-scale, high-throughput imaging by yielding data with a high spatio-temporal scale. This measurement technique will continue to have a high impact in the field of whole brain imaging due to its ability to record millions of images over the course of days or even weeks. Here we have presented a complete and detailed framework for whole mouse brain imaging. Starting with a full description of our double-sided light-sheet microscope and its constituent components we further gave details of the custom-written control software which coordinates the microscope's reliably synchronised operation. The data produced in our experiments easily amounts several TB per data set and needs to be compressed, stored, transferred, retrieved and processed necessitating the concurrent development of novel computational interface and analysis methods. Here we have presented a comprehensive, robust and fully automated pipeline of data management starting from the streaming of raw images up to the stitching of 3D data sets.

@@

Additionally another problem inherent to light-sheet microscopy degrades image quality: due to the uncoupled nature of excitation and detection in LSFM, the aberrations encountered in each arm are independent too and this can lead to a walk-off between the light-sheet and the detection FOV when large samples are imaged at depths. Adaptive optics\cite{Booth2007} provides a means to compensate for these aberrations and has recently been applied to improve LSFM\cite{Jorand2012,Wang2014}. The prospect of high quality images is especially essential for high through-put imaging methods like light-sheet microscopy and whole brain 3D reconstruction because the size of data sets are so large they warrant fully automated post processing for example for automated cell counting and identification\cite{Frasconi2014}. The effect of optical aberrations can severely obscure features even above the resolution limit and therefore hinder automated segmentation of the data. We have mounted the camera on a separate breadboard which leaves us with a lot of free, infinity-corrected space in the detection path. The implementation of adaptive optics technology into the fluorescence emission path of our LSFM in order to demonstrate real-time aberration corrected images for whole brain reconstructions will be considered in the future.
